%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.3 (29/10/16)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com) with modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,roman]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\usepackage{verbatim}
\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template
\usepackage[none]{hyphenat}
\usepackage[scale=0.82]{geometry} % Reduce document margins
\setlength{\hintscolumnwidth}{3.9cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name
\nopagenumbers{}
%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------
\firstname{Erfan} % Your first name
\familyname{Zekri Esfahani} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{CV}
\address{Artificial Intelligence Lab, Computer Engineering Dept.}{Isfahan University of Technology, Esfahan, Iran}
\mobile{(+98) 990 513 4639}
\email{erfanzekri@gmail.com}
%\emailstu{erfanzekri@ec.iut.ac.ir} 


\homepage{www.github.com/eze1376}{GitHub}
\homepageG{www.ErfanZekri.ir}{Personal WebPage}
\homepageG{www.linkedin.com/in/erfan-zekri-esfahani}{LinkedIn}

%----------------------------------------------------------------------------------------
%	CURRICULUM VITAE
%----------------------------------------------------------------------------------------
\begin{document}
\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section{Education}

\cventry{2019--Now}{M.S. in Computer Science-Artificial Intelligence and Robotics,}{ Isfahan University of Technology, Isfahan, Iran.}{}{\newline{}\textbf{Advisers:} Dr. Maziar Palhang}
{\textbf{Thesis:} "Detection and Tracking a Moving Ball using a Humanoid Robot Followed By an Immediate Kick"\newline{}\textbf{GPA: 18.06/20.}\newline{}\textbf{Selected Courses:} Pattern Recognition (20/20), Autonomous Mobile Robots (19.61/20), Computer Vision (17.8/20), Swarm Intelligence (17.83/20), Deep Learning (17.4/20) }  % Arguments not required can be left empty

\cventry{2015--2019}{B.S. in Computer Engineering-Software Engineering, }{Shahrekord University, Shahrekord, Iran.}{}{\newline{}\textbf{Adviser:} Dr. Reza Rouhani}
{\textbf{Thesis:} "Multi Kinect Sensor Fusion for Noise Reduction"\newline{}\textbf{GPA: 17.53/20.}\newline{}\textbf{Selected Courses:} Principles of Robotics (20/20), Computer Vision Fundamentals (20/20) [Class Avg.: 12.47/20], Computational Intelligence Fundamentals (19.5/20), Computer Graphics (20/20), Micro Processor (20/20) [Class Avg.:12.91/20], Operating System (20/20) [Class Avg.: 12.94/20], Computer Networks (20/20), Compiler Design Fundamentals (20/20), Formal Languages and Automata (20/20) [Class Avg.: 12/94/20], Programming Language Design (19.75/20), Signals and Systems (19/20) [Class Avg.: 11.89/20], Internet Engineering (19/20) [Class Avg.:11.67/20], Natural Language Processing (18.80/20), Database (18/20), Data Structure (18/20)} 

\cventry{2011--2015}{Diploma in Mathematics and Physics, }{Shohadaye Adab High School, Isfahan, Iran}{}{}{\textbf{GPA: 18.50/20.}} 

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------
\section{Research Interests}‎

\cvlistitem{Machine Learning}
\cvlistitem{Deep Learning}
\cvlistitem{Computer Vision}
\cvlistitem{Robotics and Humanoid Robots}


\section{Research Experience}

%----------------------------------------------------------------------------------------
%	RESEARCH EXPERIENCE SECTION
%----------------------------------------------------------------------------------------


\cventry{Nov. 2019--Now}{Graduate Research Assistant at Artificial Intelligence Labratory (AI Lab.)}{Department of Electrical and Computer Engineering, Isfahan University of Technology, Isfahan, Iran}{}{}{}




%----------------------------------------------------------------------------------------
% TEACHING EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\section{Teaching Experience}
\cvitem{Spring 2021}{‎\textbf{‎Teaching Assistant,} Autonomous Mobile Robots, \emph{Dr. Palhang, Isfahan University of Technology, Isfahan, Iran.}}
\cvitem{Fall 2020}{‎\textbf{‎Teaching Assistant,} Machine Learning, \emph{Dr. Palhang, Isfahan University of Technology, Isfahan, Iran.}}
\cvitem{Fall 2020}{‎\textbf{‎Teaching Assistant,} Introduction to Computing Systems and Programming, \emph{Mr.Zahabi, Isfahan University of Technology, Isfahan, Iran.}}
\cvitem{Spring 2019}{‎\textbf{‎Teaching Assistant,} Introduction to Computing Systems and Programming, \emph{Mrs.Moradi, Shahrekord University, Shahrekord, Iran.}}
\cvitem{Spring 2019}{‎\textbf{‎Teaching Assistant,} ‎Formal Languages and Automata, \emph{Mr.Mostafavi, Shahrekord University, Shahrekord, Iran.}}
\cvitem{Spring 2018}{‎\textbf{‎Teaching Assistant,} Formal Languages and Automata, \emph{Mr.Mostafavi, Shahrekord University, Shahrekord, Iran.}}
\cvitem{Fall 2017}{‎\textbf{‎Teaching Assistant,} Introduction to Computing Systems and Programming, \emph{Dr.Rouhani, Shahrekord University, Shahrekord, Iran.}}


%----------------------------------------------------------------------------------------
% WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
‎\section{Work Experience}

\cvitem{Jun.-Sep. 2019}{\textbf{Customer Technical Support Internship, }ICAN Engineering group, Isfahan, Iran}
\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists
\cvlistitem{Support companies' networks and their SQL databases}
\cvitem{Jul.-Oct. 2018}{\textbf{Graduation Internship, }Isfahan's Mobarakeh Steel Company, Isfahan, Iran}
\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists
\cvlistitem{Designing and developing windows application projects using C\#, WPF, ADO.NET and SQL}

‎\section{Volunteer Experience}

\cvitem{Feb. 2021}{\textbf{Content Contributor, }Facebook (Meta) Company, California, United States}
\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists
\cvlistitem{contribute in "react-native-website" repository of Facebook (Meta) Company, \href{https://github.com/facebook/react-native-website/blob/main/docs/flexbox.md}{\color{blue}\underline{\emph{Link To Repository}}}}
\cvitem{2018-2019}{\textbf{Co-Founder and Main Member of Scientific Association of Digital Games and Animation, }Shahrekord University, Shahrekord, Iran}

%----------------------------------------------------------------------------------------
% PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------
\begin{comment}
\section{Publications \& Presentations}

\cvitem{2016}{‎\textbf{G. Khalili-Zadeh-Mahani,} M.-R. Pajoohan, V. Derhami, A. Khoshnood, "Predicting Calcium Values for Gastrointestinal Bleeding Patients in Intensive Care Unit Using Clinical Variables and Fuzzy Modeling," \emph{The Journal of Shahid Sadoughi University of Medical Sciences}, vol. 24, no. 4, pp. 286-95, July 2016.}

\cvitem{2015}{\textbf{G. Khalili-Zadeh-Mahani,} M.-R. Zare-Mirakabaad and V. Derhami. "Necessity of Laboratory Blood Tests in Intensive Care Unit Using Data Mining," \emph{5th International Conference on Computer and Knowledge Engineering (ICCKE), IEEE}, Mashhad, 2015, pp. 176-180. \underline{‎\href{https://doi.org/10.1109/ICCKE.2015.7365823}{‎DOI:10.1109/ICCKE.2015.7365823}}}

\cvitem{2017}{\textbf{G. K. Mahani,} M.-R. Pajoohan, "Predicting Lab values for Gastrointestinal Bleeding Patients in the Intensive Care Unit: A Comparative Study on the Impact of Comorbidities and Medications," \emph{Artificial Intelligence in Medicine Journal},‎ \emph{(Reviewer Invited)}} 

\cvitem{2017}{A. Roshani, V. Derhami, F. Aalam, \textbf{G. Khalili-Zadeh-Mahani,} "Designing two fuzzy systems to predict unplanned feeder outages in Yazd province," \emph{Data and Knowledge Engineering Journal},‎ \emph{(with editor)} }

\cvitem{2017}{\textbf{G. K. Mahani,} V. Derhami., "Reinforcement Learning for Feature Selection", \emph{(work in progress)}}
\end{comment}
%----------------------------------------------------------------------------------------
% RESEARCH PROJECTS SECTION
%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	Professional Development SECTION
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	CERTIFICATES SECTION
%----------------------------------------------------------------------------------------

\section{Certificates}

\cvitem{Aug. 2022}{\textbf{Machine Learning:} \href{https://www.sololearn.com/certificates/course/en/4181395/1094/landscape/png}{\color{blue}\underline{\emph{Sololearn}}}}

\cvitem{Aug. 2022}{\textbf{Python Core:} \href{https://www.sololearn.com/certificates/course/en/4181395/1073/landscape/png}{\color{blue}\underline{\emph{Sololearn}}}}

\cvitem{Feb. 2019}{\textbf{SQL:} \href{https://api2.sololearn.com/v2/certificates/CT-VIXO3XG6/image/png}{\color{blue}\underline{\emph{Sololearn}}}}

\cvitem{Jun. 2018}{\textbf{JQuery:} \href{https://www.sololearn.com/Certificate/1082-4181395/jpg}{\color{blue}\underline{\emph{Sololearn}}}}


%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------
\section{Computer Skills}
\cvitem{\textbf{Programming Languages}}{\emph{Expert:} Python, C++\newline\emph{Basic:} C\#, C, MATLAB, Prolog, Assembly, Fortran, Java}
\cvitem{\textbf{AI Frameworks and Libraries}} {Darknet, OpenCV, Tensorflow, Keras, Scikit-learn, Gym}
\cvitem{\textbf{Robotics}}{ROS, Gazebo, Humanoid Robots, Raspberry Pi, Arduino}
\cvitem{\textbf{Web Development}}{ASP.NET MVC, HTML, CSS, JavaScript, Bootstrap, JQuery}
\cvitem{\textbf{Mobile Phone Development}}{React Native}
\cvitem{\textbf{Game Development}}{Unity}
\cvitem{\textbf{DBMS}}{Microsoft SQL Server, MongoDB}
\cvitem{\textbf{TypeSetting}}{Microsoft Word, \LaTeX}
\cvitem{\textbf{OS}}{Windows, Linux (Ubuntu), Raspbian OS}
\cvitem{\textbf{Others}}{Git}

‎\section{Projects}\

\cvitem{2020-Now}{\textbf{Prepare Humanoid Robots for Robocup Competition, }Isfahan University of Technology, Isfahan, Iran}
\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists
\cvlistitem{Develop Reciever for Robocup Game Controller, Create and Spawn Humanoid Robot URDF Model in Gazebo Simulation, Train a Network to Detect the Ball, Track the Ball Over Time, Develop Shoot Action for Robot (Both Simulation and Real Robot), and Implement All Algorithms on ROS1 Noetic (Simulation) and ROS2 Foxy (Real)}

\cvitem{Jun. 2022}{\textbf{COUP Board Game for Android, }Self Motivation, Isfahan, Iran}
\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists
\cvlistitem{COUP Board Game using Unity, \href{https://cafebazaar.ir/app/com.EzE.COUP}{\color{blue}\underline{\em Published in Cafebazzar (Persian App Store)}}}

\cvitem{Jul. 2020}{\textbf{Particle Filter for Autonomous Mobile Robots, }Isfahan University of Technology, Isfahan, Iran}
\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists
\cvlistitem{Particle Filter Algorithm using Python and ROS (Noetic), \href{https://github.com/eze1376/Particle_filter}{\color{blue}\underline{\em Source Code in Github}}}

\cvitem{Aug. 2019}{\textbf{Sudoku Solver for Android, }Self Motivation, Isfahan, Iran}
\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists
\cvlistitem{Sudoku Solver Application using React-Native, \href{https://cafebazaar.ir/app/com.sudoku}{\color{blue}\underline{\em Published in Cafebazzar (Persian App Store)}}}

\cvitem{Jun. 2019}{\textbf{Depth Detection with Stereo Camera, }Shahrekord University, Shahrekord, Iran}
\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists
\cvlistitem{Compute Depth of Several Spherical Objects with Two Images using MATLAB, Circle Hough Transform Algorithm, and Triangulation (Computer Vision Course Project)}

\cvitem{Jun. 2019}{\textbf{Simulation of an Autonomous Car to Find a Specific Black Colored Square, }Shahrekord University, Shahrekord, Iran}
\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists
\cvlistitem{Compute Car Wheel Speeds and Positions (as Servo Motors) to Search Whole Area to Find a Specific Black Colored Square (Robotics Course Project)}

\cvitem{Jun. 2019}{\textbf{Simulation of a Mechanical Arm to Move Objects, }Shahrekord University, Shahrekord, Iran}
\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists
\cvlistitem{Compute Joint Angles of a Mechanical Arm to Go to a Specific Point using Forward Kinematic (Robotics Course Project)}

\cvitem{Jan. 2019}{\textbf{Noise Canceling for Human Voices, }Shahrekord University, Shahrekord, Iran}
\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists
\cvlistitem{Cancel Environment Noises using Low/High Pass Filter with MATLAB (Signal Processing Course Project)}

\cvitem{Jan. 2019}{\textbf{Iris Flower Classification, }Shahrekord University, Shahrekord, Iran}
\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists
\cvlistitem{Classify Iris Flowers using Python and Scikit-learn Library (Computational Intelligence Course Project)}

\cvitem{Jan. 2019}{\textbf{Author's Gender Classification, }Shahrekord University, Shahrekord, Iran}
\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists
\cvlistitem{Classify Author's Gender using Python and Scikit-learn Library (Natural Language Processing Course Project)}

\cvitem{Jun. 2019}{\textbf{Weightlifting Game for Windows, }Shahrekord University, Shahrekord, Iran}
\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists
\cvlistitem{Weightlifting Game using C++ and DirectX Library (Graphics Course Project), \href{https://github.com/eze1376/Weightlifting_Game_DirectX}{\color{blue}\underline{\em Source Code in Github}}}

\cvitem{Jun. 2018}{\textbf{Redevelopment of Cinematicket Website, }Shahrekord University, Shahrekord, Iran}
\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists
\cvlistitem{Redevelopment of Sell/Buy Cinema and Theater Tickets Website (\href{https://cinematicket.org/}{\color{blue}\underline{\em Cinematicket}}) using HTML, CSS, Javascript, Json, Ajax, and Bootstrap (Internet Engineering Course Final-term Project)}

\cvitem{Mar. 2018}{\textbf{Minesweeper Game for the Web, }Shahrekord University, Shahrekord, Iran}
\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists
\cvlistitem{Minesweeper Game using HTML, CSS, Javascript, and Bootstrap (Internet Engineering Course Mid-term Project), \href{https://eze1376.github.io/Htmls/FindTheMine.html}{\color{blue}\underline{\em Play Game Online}}}

\cvitem{Dec. 2017}{\textbf{Tic-Tac-Toe Game for Android, }Shahrekord University, Shahrekord, Iran}
\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists
\cvlistitem{Smart Tic-Tac-Toe Game using Unity, C\#, and Minimax Algorithm (AI Course Project)}

\cvitem{Aug. 2017}{\textbf{Simple Action and Intellectual Games for Windows, }Self Motivation, Isfahan, Iran}
\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists
\cvlistitem{Several Simple Games using Unity and C\#}

\cvitem{Aug. 2016}{\textbf{Flappy Bird Game for Windows, }Self Motivation, Isfahan, Iran}
\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists
\cvlistitem{Develop Flappy Bird Game using C++, SDL extention, and Physics Motion Formulas}

\cvitem{Apr. 2016}{\textbf{Car Number-Plate Recognition, }Shahrekord University, Shahrekord, Iran}
\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists
\cvlistitem{Recogniton of Simple Handmade Number-Plates using C++, SDL extention, and pixel-wise processing}

\cvitem{Mar. 2016}{\textbf{Windows Paint, }Shahrekord University, Shahrekord, Iran}
\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists
\cvlistitem{Windows Paint Application using C++ and SDL extention}

\cvitem{Jan. 2016}{\textbf{Reserve Food System (in Terminal), }Shahrekord University, Shahrekord, Iran}
\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists
\cvlistitem{Reserve and Consume Food Coupons in University's Dinning Salon as a simulation, \href{https://github.com/eze1376/ReserveFoodService}{\color{blue}\underline{\em Source Code in Github}}}

\section{Honors \& Awards}
‎‎%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%---------------------------------------------------------------------------------------
\cvitem{2020}{\textbf{Ranked 1\textsuperscript{st}} in \href{https://www.digikala.com/}{\color{blue}{\underline{\em Digikala}}} (Biggest Online Store in Iran) Artificial Intelligence (AI) Challenge, Isfahan University of Technology, Isfahan, Iran}

\cvitem{2019}{\textbf{Talented Student Award:} Qualified for graduate studies in Isfahan University of Technology, Isfahan University, and Shiraz University without entrance exam, Iran}

\cvitem{2019}{\textbf{Ranked 2\textsuperscript{nd}} among Computer Engineering students in all 8 semesters, Shahrekord University, Shahrekord, Iran}

\cvitem{2016}{\textbf{Ranked 2\textsuperscript{nd}} in ACM intra-university Contest, Shahrekord University, Shahrekord, Iran}

\cvitem{2007}{\textbf{Ranked in top 2\% in the B. S. Nationwide Universities Entrance Exam,} Physics and Mathematics Diploma, Iran}


%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------
\section{Languages}
\cvitem{\textbf{English}}{Professional Working Proficiency}
\cvitem{\textbf{Persian}}{Native Language}

\section{Hobbies}
\cvitem{}{\begin{itemize}
		\item Reading Books
		\item Playing Soccer
		\item Playing Video Games
		\item Swimming
		\item Playing Badminton
	\end{itemize}}


\end{document}